### 2025-09-23 paper/sec/authoring-workflow.tex
Rehashing workflow description.

\item \textbf{Initial configuration.} The author imports the target text and accompanying data into the
system, creating a programmatic representation of the target document. Initially this is simply isomorphic to
the target text, taking the form of a string literal \kw{"""..."""}, where the triple quotes are Fluid syntax
for a Python or JavaScript-style \emph{interpolated string}, i.e.~a literal where expressions of the form
\kw{\{$e$\}} are permitted within the string. The \SuggestionAgent analyses these inputs and identifies any
fragments of natural language which are candidates for being computed instead of remaining as literal
substrings.

\item \textbf{High-level Authoring workflow.} The system then enters the human-in-the loop authoring workflow
shown in Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The
system initially waits for the author to select a fragment of text $s$ to interpret (perhaps but not
necessarily highlighted by the \SuggestionAgent). The system then attempts to generates a candidate Fluid
expression $e$ using the closed-loop synthesis step (3) below. If this process succeeds with an expression
$e$, the system proceeds to the manual validation step (4) below. If the code generation step fails with no
expression, no remedial action is open to the author; this is considered an unsuccessful path through the
workflow and returns the system to the start state. Otherwise the code generation step fails with a mismatched
string $s' \neq s$ outcome, and the user can choose to manually abort and return to the entry state, or
optionally to \emph{revise the goal}, replacing $s$ with $s'$ in the target document and retaining $e$ as the
candidate expression. This is intended to cover the situation where the author has made a claim which is
\emph{incorrect}, but the data set and surrounding natural language has caused the LLM to synthesise an
expression which generates a different value from the one specified by the user.

\item \textbf{Code synthesis step.} The expression synthesis step is itself an internal loop which starts with
an initial prompt sent to the LLM (\secref{prompt-design} below) requesting the generation of an expression
$e$. Using the Fluid command-line interface, the expression is validated by checking that it evaluates without
error, produces a value coercible to a string $s'$, and finally that $s'$ is equal to the target fragment $s$.
Any failure triggers prompt augmentation with the appropriate error message and the system retries generation.
If code synthesis loop is able to yield an expression which computes $s$ within a maximum number of retries,
the synthesis step succeeds with $e$. If the last generated $e$ was invalid (resulting in an error), the code
synthesis step fails with no expression. Otherwise, the code synthesis fails with a mismatched string outcome.

>>>>

\item \textbf{Initial configuration.} The author imports the target text and accompanying data into the system
to create a programmatic representation of the target document. Initially this is simply isomorphic to the
target text, taking the form of a string literal \kw{"""..."""}, where the triple quotes are Fluid syntax for
a Python or JavaScript-style \emph{interpolated string}, i.e.~a literal where expressions of the form
\kw{\{$e$\}} are permitted within the string. The \SuggestionAgent analyses the target text and identifies any
fragments which are candidates for being computed instead of remaining as literal substrings.

\item \textbf{High-level Authoring workflow.} The system then enters the human-in-the loop authoring workflow
shown in Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The
system waits for the author to select a fragment of text $s$ to interpret (perhaps previously highlighted by
the \SuggestionAgent). The system then attempts to generates a candidate Fluid expression $e$ using the
closed-loop synthesis step (3) below. If code synthesis succeeds with an expression $e$, the system proceeds
to the manual validation step (4) below. If the synthesis step fails with no expression, no remedial action is
possible; this is considered an unsuccessful path through the workflow and returns the system to the entry
state. Otherwise the synthesis step produces an expression $e$ which evaluates to a mismatched string $s' \neq
s$ outcome, and the user can choose to manually abort and return to the entry state, or optionally to
\emph{revise the goal}, replacing $s$ with $s'$ in the target document and retaining $e$ as the candidate
expression. This is intended to cover the situation where the author has made a claim which is
\emph{incorrect}, and the data set and surrounding natural language have led the LLM to synthesise an
expression which generates a different value from the one specified by the user.

\item \textbf{Code synthesis step.} The expression synthesis step is an internal loop which starts with an
initial prompt sent to the LLM (\secref{prompt-design} below) requesting the generation of an expression $e$.
Using the Fluid command-line interface, the expression is validated to check that it evaluates without error,
produces a value coercible to a string $s'$, and finally that $s'$ is equal to the target fragment $s$. Any
failure triggers prompt augmentation with the appropriate error message and the system retries generation. If
code synthesis loop is able to yield an expression which computes $s$ within a maximum number of retries, the
synthesis step succeeds with $e$. If the last generated $e$ was invalid (resulting in an error), the code
synthesis step fails with no expression. Otherwise, code synthesis produces an expression $e$ but with a
mismatched string outcome $s' \neq s$.
